
\documentclass{article}
\usepackage[margin=0.5in]{geometry}  % Set custom margin size
\usepackage{xcolor}
\setlength{\parindent}{0pt}  % Disable paragraph indentation
\begin{document}
\small  % Set text to smaller size
\definecolor{Bocas}{HTML}{648FFF}
\definecolor{SoCal}{HTML}{FFB000}
\definecolor{Leigh}{HTML}{785EF0}
\definecolor{Lizard}{HTML}{FE6100}
\definecolor{Colleague}{HTML}{DC267F}
1. \textbf{Bairdioidea}: \textcolor{Bocas}{\textit{Bairdoppilata hirsuta}}, \textcolor{Bocas}{\textit{B. sp.}}, \textcolor{SoCal}{\textit{B. verdesensis}}, \textcolor{Leigh}{\textit{Bythocyprididae sp}}, \textcolor{Bocas}{\textit{Bythocypris promoza}}, \textcolor{Bocas}{\textit{Zabythocypris helicina}}, \textcolor{Leigh}{\textit{Anchistrocheles}} 2. \textbf{Cylindroleberidoidea}: \textcolor{Bocas}{\textit{Actinoseta chelisparsa}}, \textcolor{Bocas}{\textit{A. hummelincki}}, \textcolor{Bocas}{\textit{Amboleberis americana}}, \textcolor{Bocas}{\textit{Asteropella kaufmani}}, \textcolor{Bocas}{\textit{Asteropterygion oculitristis}}, \textcolor{Bocas}{\textit{cf Parasterope}}, \textcolor{Bocas}{\textit{Cylindroleberidae sp1 }}, \textcolor{Bocas}{\textit{C. sp2}} 3. \textbf{Cypridinoidea}: \textcolor{Leigh}{\textit{Common one}}, \textcolor{Bocas}{\textit{Fred MFU}}, \textcolor{Bocas}{\textit{Jimmorinia gunnari}}, \textcolor{Bocas}{\textit{Maristella MGL}}, \textcolor{Bocas}{\textit{Photeros EGD}}, \textcolor{Bocas}{\textit{P. NOL}}, \textcolor{Bocas}{\textit{P. SFM}}, \textcolor{Bocas}{\textit{Skogsbergia lerneri}}, \textcolor{Bocas}{\textit{S. sp G}}, \textcolor{Bocas}{\textit{S. sp H}}, \textcolor{Bocas}{\textit{S. sp I}}, \textcolor{Bocas}{\textit{S. sp. A}}, \textcolor{Bocas}{\textit{S. sp. B}}, \textcolor{Bocas}{\textit{S. sp. C}}, \textcolor{Bocas}{\textit{S. sp. D}}, \textcolor{Bocas}{\textit{S. sp. E}}, \textcolor{Bocas}{\textit{S. sp. F}} 4. \textbf{Cypridoidea}: \textcolor{Bocas}{\textit{Parapontoparta spicacarens}} 5. \textbf{Cytherelloidea}: \textcolor{SoCal}{\textit{Cytherelloidea californica}}, \textcolor{Lizard}{\textit{Keijcyoidea poikilokosmena}} 6. \textbf{Cytheroidea}: \textcolor{Lizard}{\textit{Bythocythere arenicola}}, \textcolor{Lizard}{\textit{Corallicythere arcanis}}, \textcolor{SoCal}{\textit{Cythere maia}}, \textcolor{Lizard}{\textit{Microcytherura aestuaricola}}, \textcolor{Lizard}{\textit{Cyprideis australiensis}}, \textcolor{Bocas}{\textit{Megacythere punctocostata}}, \textcolor{Lizard}{\textit{Paracytheroma aestatophfla}}, \textcolor{Lizard}{\textit{Cytherura cf. densuireticulata}}, \textcolor{SoCal}{\textit{Hemicytherura santosensis}}, \textcolor{Lizard}{\textit{H. viridiminor}}, \textcolor{Lizard}{\textit{Semicytherura sp. L1}}, \textcolor{Bocas}{\textit{Cytheropteron assimiloides}}, \textcolor{Leigh}{\textit{C. sp1}}, \textcolor{Leigh}{\textit{Hemicytherura cf. costallata}}, \textcolor{Bocas}{\textit{Semicytherura johnsonoides}}, \textcolor{Bocas}{\textit{Xylocythere rimosa}}, \textcolor{SoCal}{\textit{Ambostracon glacum}}, \textcolor{SoCal}{\textit{Aurila lincolnensis}}, \textcolor{Leigh}{\textit{Bradleya sp}}, \textcolor{SoCal}{\textit{Caudites acosaguensis}}, \textcolor{Leigh}{\textit{Cythereis joanae}}, \textcolor{Bocas}{\textit{Hemicythere sp.}}, \textcolor{Leigh}{\textit{Pterygocythere sp}}, \textcolor{Lizard}{\textit{Parakrithella sp. L1}}, \textcolor{Lizard}{\textit{P. sp. L2}}, \textcolor{Bocas}{\textit{Limnocythere sanctipatricii}}, \textcolor{Lizard}{\textit{Loxoconcha heronislandensis}}, \textcolor{Lizard}{\textit{L. insulaecapricornensis}}, \textcolor{SoCal}{\textit{L. lenticulata}}, \textcolor{Lizard}{\textit{L. parahuahineensis}}, \textcolor{Bocas}{\textit{L. sp.}}, \textcolor{SoCal}{\textit{L. sp1}}, \textcolor{Lizard}{\textit{L. violacea}}, \textcolor{Lizard}{\textit{Loxoconchella lizardensis}}, \textcolor{Lizard}{\textit{Loxocorniculum georgei}}, \textcolor{Leigh}{\textit{Copytus cf. novaezealandiae}}, \textcolor{Lizard}{\textit{Paracytheridea gynaikokratia}}, \textcolor{Lizard}{\textit{P. sp. L1}}, \textcolor{Leigh}{\textit{cf Paradoxostoma }}, \textcolor{Lizard}{\textit{Paradoxostoma aculeatum}}, \textcolor{Lizard}{\textit{P. angulatum}}, \textcolor{Lizard}{\textit{P. cf. navicula}}, \textcolor{Lizard}{\textit{P. congruens}}, \textcolor{Lizard}{\textit{P. fuscumaculosum}}, \textcolor{Lizard}{\textit{P. heronislandense}}, \textcolor{Lizard}{\textit{P. kurrawa}}, \textcolor{Lizard}{\textit{P. lizardense}}, \textcolor{Lizard}{\textit{P. maldum }}, \textcolor{Lizard}{\textit{P. melania }}, \textcolor{Lizard}{\textit{P. minya}}, \textcolor{Lizard}{\textit{P. moonga}}, \textcolor{Lizard}{\textit{P. sp. L1}}, \textcolor{Lizard}{\textit{P. sp. L2}}, \textcolor{SoCal}{\textit{P. sp1}}, \textcolor{SoCal}{\textit{P. striungulum}}, \textcolor{Lizard}{\textit{P. tininarrin}}, \textcolor{Lizard}{\textit{P. virgatum }}, \textcolor{Lizard}{\textit{P. waminoa}}, \textcolor{Lizard}{\textit{P. worooa}}, \textcolor{Lizard}{\textit{Keijia hirundo}}, \textcolor{Lizard}{\textit{Kotoracythere inconspicua}}, \textcolor{Lizard}{\textit{Mckenziartia foveata}}, \textcolor{Leigh}{\textit{Munseyalla}}, \textcolor{Bocas}{\textit{Thaerocythere sp.}}, \textcolor{Bocas}{\textit{Trachyleberis sp.}}, \textcolor{SoCal}{\textit{Xestoleberis hopkinsi Skogsberg}}, \textcolor{SoCal}{\textit{X. scammonensis}}, \textcolor{Bocas}{\textit{X. sp.}}, \textcolor{SoCal}{\textit{X. sp1}}, \textcolor{SoCal}{\textit{X. sp2}} 7. \textbf{Darwinuloidea}: \textcolor{Bocas}{\textit{Vestalenula sp}} 8. \textbf{Halocypridoidea }: \textcolor{Bocas}{\textit{Proceroecia convexa}} 9. \textbf{Macrocypridoidea }: \textcolor{SoCal}{\textit{Macrocyprina barbara}}, \textcolor{Bocas}{\textit{Macropyxis kaesleri}} 10. \textbf{Polycopoidea }: \textcolor{Leigh}{\textit{Polycope sp1}} 11. \textbf{Pontocypridoidea}: \textcolor{Bocas}{\textit{Pontocypris sp.}} 12. \textbf{Punciodea}: \textcolor{Leigh}{\textit{Manawa staceyi}} 13. \textbf{Sarsielloidea}: \textcolor{Bocas}{\textit{Philomedidae sp}}, \textcolor{Bocas}{\textit{Rutiderma hartmanni}}, \textcolor{SoCal}{\textit{R. judayi}}, \textcolor{SoCal}{\textit{R. rotundum}}, \textcolor{Bocas}{\textit{Rutidermata darbyi cf}}, \textcolor{Bocas}{\textit{Rutidermatidae sp. 1}}, \textcolor{Bocas}{\textit{R. sp. 2}}, \textcolor{Bocas}{\textit{Sarsiellidae sp 1}}, \textcolor{Bocas}{\textit{S. sp 2}}, \textcolor{Bocas}{\textit{S. sp 3}}, \textcolor{Bocas}{\textit{S. sp 4}}, \textcolor{Bocas}{\textit{S. sp 5}}, \textcolor{Bocas}{\textit{S. sp 6}}, \textcolor{Bocas}{\textit{S. sp 7}} 14. \textbf{Sigillioidea}: \textcolor{Bocas}{\textit{Cardobairdia sp. 36}}, \textcolor{Bocas}{\textit{Saipanetta cf. sp. 31}}, \textcolor{Bocas}{\textit{Saipanettidae cf. sp. 56}}, \textcolor{Bocas}{\textit{S. sp. 66}} 15. \textbf{Terrestricytheroidea}: \textcolor{Colleague}{\textit{Terrestricythere elisabethae}} 16. \textbf{Thaumatocypridoidea}: \textcolor{Colleague}{\textit{Thaumatocypris sp}}
\end{document}
